---
title: "IGF1R and survival curves"
---

```{r global, message = FALSE, warning = FALSE, echo = FALSE}
source("global.R")
attach(DF)
```

# **Median H-scores**
## Tumor recurrence
```{r h_group_median.recurrence}
status <- h_group_median
g_surv(fu_recurrence, recurrence, status)
```

***

## Tumor progression
```{r h_group_median.progression}
g_surv(fu_progression, progression, status)
```

***

## Overall mortality
```{r h_group_median.dead}
g_surv(fu_progression, dead, status)
```

***

## Cancer-related mortality
```{r h_group_median.dod}
g_surv(fu_progression, dod, status)
```

***

# **Maximum H-scores**
## Tumor recurrence
```{r h_group_max.recurrence}
status <- h_group_max
g_surv(fu_recurrence, recurrence, status)
```

***

## Tumor progression
```{r h_group_max.progression}
g_surv(fu_progression, progression, status)
```

***

## Overall mortality
```{r h_group_max.dead}
g_surv(fu_progression, dead, status)
```

***

## Cancer-related mortality
```{r h_group_max.dod}
g_surv(fu_progression, dod, status)
```

***

# **Median HER2 scores**
## Tumor recurrence
```{r her2_group_median.recurrence}
status <- her2_group_median
g_surv(fu_recurrence, recurrence, status)
```

***

## Tumor progression
```{r her2_group_median.progression}
g_surv(fu_progression, progression, status)
```

***

## Overall mortality
```{r her2_group_median.dead}
g_surv(fu_progression, dead, status)
```

***

## Cancer-related mortality
```{r her2_group_median.dod}
g_surv(fu_progression, dod, status)
```

***

# **Maximum HER2 scores**
## Tumor recurrence
```{r her2_group_max.recurrence}
status <- her2_group_max
g_surv(fu_recurrence, recurrence, status)
```

***

## Tumor progression
```{r her2_group_max.progression}
g_surv(fu_progression, progression, status)
```

***

## Overall mortality
```{r her2_group_max.dead}
g_surv(fu_progression, dead, status)
```

***

## Cancer-related mortality
```{r her2_group_max.dod}
g_surv(fu_progression, dod, status)
```

***

