---
title: "Regression by IGF1R positivity"
editor_options: 
  chunk_output_type: console
---

```{r global, message=FALSE, warning=FALSE, echo=FALSE}
source("global.R")

# Libraries
library(survival)
```

***

# Tumor progression
## Unadjusted model
```{r unadjusted_progression}
# Age
mdl_unadj <- coxph(
  Surv(fu_progression, as.numeric(progression)) ~ age,
  data = DF
)
sum_mdl_unadj <- summary(mdl_unadj)
mdl_tbl_unadj <- t(c(
    sum_mdl_unadj$conf.int[ , -2],
    sum_mdl_unadj$coefficients[ , 5]
    )) %>% 
    formatC(digits = 2, format = "fg") %>% 
    data.frame()
rownames(mdl_tbl_unadj) <- c("Age, per 1 year increase")
unadj_age <- mdl_tbl_unadj

# Sex
mdl_unadj <- coxph(
  Surv(fu_progression, as.numeric(progression)) ~ sex,
  data = DF
)
sum_mdl_unadj <- summary(mdl_unadj)
mdl_tbl_unadj <- t(c(
    sum_mdl_unadj$conf.int[ , -2],
    sum_mdl_unadj$coefficients[ , 5]
    )) %>% 
    formatC(digits = 2, format = "fg") %>% 
    data.frame()
rownames(mdl_tbl_unadj) <- c("Sex: Female vs Male")
unadj_sex <- mdl_tbl_unadj

# Location
mdl_unadj <- coxph(
  Surv(fu_progression, as.numeric(progression)) ~ location,
  data = DF
)
sum_mdl_unadj <- summary(mdl_unadj)
mdl_tbl_unadj <- cbind(
    sum_mdl_unadj$conf.int[ , -2],
    sum_mdl_unadj$coefficients[ , 5]
    ) %>% 
    formatC(digits = 2, format = "fg") %>% 
    data.frame()
rownames(mdl_tbl_unadj) <- c(
    "Location: Ureter vs Pelvis",
    "Location: Pelvis-ureter vs Pelvis"
)
unadj_location <- mdl_tbl_unadj

# pT stage
mdl_unadj <- coxph(
  Surv(fu_progression, as.numeric(progression)) ~ high_pt,
  data = DF
)
sum_mdl_unadj <- summary(mdl_unadj)
mdl_tbl_unadj <- t(c(
    sum_mdl_unadj$conf.int[ , -2],
    sum_mdl_unadj$coefficients[ , 5]
    )) %>% 
    formatC(digits = 2, format = "fg") %>% 
    data.frame()
rownames(mdl_tbl_unadj) <- c(
    "pT stage: High stage vs Low stage"
)
unadj_pt <- mdl_tbl_unadj

# WHO Grade (NOT INCLUDED DUE TO INFINITE BETA)
# mdl_unadj <- coxph(
#   Surv(fu_progression, as.numeric(progression)) ~ high_grade,
#   data = DF
# )
# sum_mdl_unadj <- summary(mdl_unadj)
# mdl_tbl_unadj <- t(c(
#     sum_mdl_unadj$conf.int[ , -2],
#     sum_mdl_unadj$coefficients[ , 5]
#     )) %>% 
#     formatC(digits = 2, format = "fg") %>% 
#     data.frame()
# rownames(mdl_tbl_unadj) <- c(
#     "WHO Grade: High grade vs low grade"
# )
# unadj_grade <- mdl_tbl_unadj

# Lymphovascular invasion
mdl_unadj <- coxph(
  Surv(fu_progression, as.numeric(progression)) ~ lvi,
  data = DF
)
sum_mdl_unadj <- summary(mdl_unadj)
mdl_tbl_unadj <- t(c(
    sum_mdl_unadj$conf.int[ , -2],
    sum_mdl_unadj$coefficients[ , 5]
    )) %>% 
    formatC(digits = 2, format = "fg") %>% 
    data.frame()
rownames(mdl_tbl_unadj) <- c(
    "Lymphovascular invasion: Present vs Absent"
)
unadj_lvi <- mdl_tbl_unadj

# Lymph nodes metastasis
mdl_unadj <- coxph(
  Surv(fu_progression, as.numeric(progression)) ~ lymph_nodes,
  data = DF
)
sum_mdl_unadj <- summary(mdl_unadj)
mdl_tbl_unadj <- t(c(
    sum_mdl_unadj$conf.int[ , -2],
    sum_mdl_unadj$coefficients[ , 5]
    )) %>% 
    formatC(digits = 2, format = "fg") %>% 
    data.frame()
rownames(mdl_tbl_unadj) <- c(
    "Lymph nodes metastasis: Present vs Absent"
)
unadj_lymph_nodes <- mdl_tbl_unadj

# IFG1R
mdl_unadj <- coxph(
  Surv(fu_progression, as.numeric(progression)) ~ igf1r_exprs,
  data = DF
)
sum_mdl_unadj <- summary(mdl_unadj)
mdl_tbl_unadj <- t(c(
    sum_mdl_unadj$conf.int[ , -2],
    sum_mdl_unadj$coefficients[ , 5]
    )) %>% 
    formatC(digits = 2, format = "fg") %>% 
    data.frame()
rownames(mdl_tbl_unadj) <- c(
    "IGF1R: Positive vs Negative"
)
unadj_ifg1r_exprs <- mdl_tbl_unadj

# Merging tables
mdl_tbl_unadj <- rbind(
    unadj_age,
    unadj_sex,
    unadj_location,
    unadj_pt,
#    unadj_grade,
    unadj_lvi,
    unadj_lymph_nodes,
    unadj_ifg1r_exprs
)

# Final table
kable(
    mdl_tbl_unadj,
    col.names = c("HR", "Lower .95", "Upper .95", "P value"),
    align = c("c")
)
```

**Note:** WHO grade was not included in the regression model for tumor progression due to the absence of low-grade cases that progressed.

***

## Adjusted model
```{r adjusted_progression}
mdl <- coxph(
  Surv(fu_progression, as.numeric(progression)) ~ 
      age + 
      sex + 
      location + 
      high_pt + 
#      high_grade + 
      lvi + 
      lymph_nodes + 
      igf1r_exprs,
  data = DF
)

sum_mdl <- summary(mdl)

mdl_tbl <- cbind(
    sum_mdl$conf.int[ , -2],
    sum_mdl$coefficients[ , 5]
)

rownames(mdl_tbl) <- c(
    "Age, per 1 year increase",
    "Sex: Female vs Male",
    "Location: Ureter vs Pelvis",
    "Location: Pelvis-ureter vs Pelvis",
    "pT stage: High stage vs Low stage",
#    "WHO Grade: High grade vs low grade",
    "Lymphovascular invasion: Present vs Absent",
    "Lymph nodes metastasis: Present vs Absent",
    "IGF1R: Positive vs Negative"
)

kable(
    formatC(mdl_tbl, digits = 2, format = "fg"),
    col.names = c("HR", "Lower .95", "Upper .95", "P value"),
    align = c("c")
)
```

**Note:** WHO grade was not included in the regression model for tumor progression due to the absence of low-grade cases that progressed.

***

# Cancer-specific mortality
## Unadjusted model
```{r unadjusted_dod}
# Age
mdl_unadj <- coxph(
  Surv(fu_progression, as.numeric(dod)) ~ age,
  data = DF
)
sum_mdl_unadj <- summary(mdl_unadj)
mdl_tbl_unadj <- t(c(
    sum_mdl_unadj$conf.int[ , -2],
    sum_mdl_unadj$coefficients[ , 5]
    )) %>% 
    formatC(digits = 2, format = "fg") %>% 
    data.frame()
rownames(mdl_tbl_unadj) <- c("Age, per 1 year increase")
unadj_age <- mdl_tbl_unadj

# Sex
mdl_unadj <- coxph(
  Surv(fu_progression, as.numeric(dod)) ~ sex,
  data = DF
)
sum_mdl_unadj <- summary(mdl_unadj)
mdl_tbl_unadj <- t(c(
    sum_mdl_unadj$conf.int[ , -2],
    sum_mdl_unadj$coefficients[ , 5]
    )) %>% 
    formatC(digits = 2, format = "fg") %>% 
    data.frame()
rownames(mdl_tbl_unadj) <- c("Sex: Female vs Male")
unadj_sex <- mdl_tbl_unadj

# Location
mdl_unadj <- coxph(
  Surv(fu_progression, as.numeric(dod)) ~ location,
  data = DF
)
sum_mdl_unadj <- summary(mdl_unadj)
mdl_tbl_unadj <- cbind(
    sum_mdl_unadj$conf.int[ , -2],
    sum_mdl_unadj$coefficients[ , 5]
    ) %>% 
    formatC(digits = 2, format = "fg") %>% 
    data.frame()
rownames(mdl_tbl_unadj) <- c(
    "Location: Ureter vs Pelvis",
    "Location: Pelvis-ureter vs Pelvis"
)
unadj_location <- mdl_tbl_unadj

# pT stage
mdl_unadj <- coxph(
  Surv(fu_progression, as.numeric(dod)) ~ high_pt,
  data = DF
)
sum_mdl_unadj <- summary(mdl_unadj)
mdl_tbl_unadj <- t(c(
    sum_mdl_unadj$conf.int[ , -2],
    sum_mdl_unadj$coefficients[ , 5]
    )) %>% 
    formatC(digits = 2, format = "fg") %>% 
    data.frame()
rownames(mdl_tbl_unadj) <- c(
    "pT stage: High stage vs Low stage"
)
unadj_pt <- mdl_tbl_unadj

# WHO Grade
mdl_unadj <- coxph(
  Surv(fu_progression, as.numeric(dod)) ~ high_grade,
  data = DF
)
sum_mdl_unadj <- summary(mdl_unadj)
mdl_tbl_unadj <- t(c(
    sum_mdl_unadj$conf.int[ , -2],
    sum_mdl_unadj$coefficients[ , 5]
    )) %>%
    formatC(digits = 2, format = "fg") %>%
    data.frame()
rownames(mdl_tbl_unadj) <- c(
    "WHO Grade: High grade vs low grade"
)
unadj_grade <- mdl_tbl_unadj

# Lymphovascular invasion
mdl_unadj <- coxph(
  Surv(fu_progression, as.numeric(dod)) ~ lvi,
  data = DF
)
sum_mdl_unadj <- summary(mdl_unadj)
mdl_tbl_unadj <- t(c(
    sum_mdl_unadj$conf.int[ , -2],
    sum_mdl_unadj$coefficients[ , 5]
    )) %>% 
    formatC(digits = 2, format = "fg") %>% 
    data.frame()
rownames(mdl_tbl_unadj) <- c(
    "Lymphovascular invasion: Present vs Absent"
)
unadj_lvi <- mdl_tbl_unadj

# Lymph nodes metastasis
mdl_unadj <- coxph(
  Surv(fu_progression, as.numeric(dod)) ~ lymph_nodes,
  data = DF
)
sum_mdl_unadj <- summary(mdl_unadj)
mdl_tbl_unadj <- t(c(
    sum_mdl_unadj$conf.int[ , -2],
    sum_mdl_unadj$coefficients[ , 5]
    )) %>% 
    formatC(digits = 2, format = "fg") %>% 
    data.frame()
rownames(mdl_tbl_unadj) <- c(
    "Lymph nodes metastasis: Present vs Absent"
)
unadj_lymph_nodes <- mdl_tbl_unadj

# IFG1R
mdl_unadj <- coxph(
  Surv(fu_progression, as.numeric(dod)) ~ igf1r_exprs,
  data = DF
)
sum_mdl_unadj <- summary(mdl_unadj)
mdl_tbl_unadj <- t(c(
    sum_mdl_unadj$conf.int[ , -2],
    sum_mdl_unadj$coefficients[ , 5]
    )) %>% 
    formatC(digits = 2, format = "fg") %>% 
    data.frame()
rownames(mdl_tbl_unadj) <- c(
    "IGF1R: Positive vs Negative"
)
unadj_ifg1r_exprs <- mdl_tbl_unadj

# Merging tables
mdl_tbl_unadj <- rbind(
    unadj_age,
    unadj_sex,
    unadj_location,
    unadj_pt,
    unadj_grade,
    unadj_lvi,
    unadj_lymph_nodes,
    unadj_ifg1r_exprs
)

# Final table
kable(
    mdl_tbl_unadj,
    col.names = c("HR", "Lower .95", "Upper .95", "P value"),
    align = c("c")
)
```


## Adjusted model
```{r adjusted_dod}
mdl <- coxph(
  Surv(fu_progression, as.numeric(dod)) ~ 
      age + 
      sex + 
      location + 
      high_pt + 
      high_grade + 
      lvi + 
      lymph_nodes + 
      igf1r_exprs,
  data = DF
)

sum_mdl <- summary(mdl)

mdl_tbl <- cbind(
    sum_mdl$conf.int[ , -2],
    sum_mdl$coefficients[ , 5]
)

rownames(mdl_tbl) <- c(
    "Age, per 1 year increase",
    "Sex: Female vs Male",
    "Location: Ureter vs Pelvis",
    "Location: Pelvis-ureter vs Pelvis",
    "pT stage: High stage vs Low stage",
    "WHO Grade: High grade vs low grade",
    "Lymphovascular invasion: Present vs Absent",
    "Lymph nodes metastasis: Present vs Absent",
    "IGF1R: Positive vs Negative"
)

kable(
    formatC(mdl_tbl, digits = 2, format = "fg"),
    col.names = c("HR", "Lower .95", "Upper .95", "P value"),
    align = c("c")
)
```

